preprocess_human_recognition

### 2021-06-14 analysis/step4b_download_recognition_data/preprocess_recognition_data.Rmd
scripts to preprocesss recognition data

```{r}
d <- read.csv("csv_out/Devphotodraw_recognition_pilot.csv") %>%
  as.tibble() %>%
  mutate(image_name_short = str_split_fixed(imageName,'object_drawings/',2)[,2]) %>%
  mutate(age_temp = str_split_fixed(image_name_short,'age',2)[,2]) %>%
  mutate(age = as.numeric(str_split_fixed(age_temp,'_',2)[,1]))
```

>>>>

# compile all output csvs
```{r}
all_data=as_tibble()
for (batch in range(1,2)){
  this_batch = read.csv(paste0("csv_out/Devphotodraw_recognition_batch",batch,".csv")) %>% as_tibble() 
  all_data <- rbind(all_data, this_batch)
}

```

# preprocess image name / age
```{r}
d <- all_data %>%
  mutate(image_name_short = str_split_fixed(imageName,'object_drawings/',2)[,2]) %>%
  mutate(age_temp = str_split_fixed(image_name_short,'age',2)[,2]) %>%
  mutate(age = as.numeric(str_split_fixed(age_temp,'_',2)[,1]))
```
